Model LF

### 2022-10-27 max_dp endogen stød.Rmd
Commit

ik_disc = disc_bs$simulation$ik
```

@@

ik_disc_01 = disc_S1$simulation$ik
```

@@

```{r}
plot(((yk_ds_02 - yk_ds_00) / yk_ds_00), col= "black", xlab= "Year", ylab= "% Change in gdp", main= "GDP");

grid()
```

>>>>

ik_disc = disc_bs$simulation$ik
c_ratio= pconk_ds_disc/yk_ds_disc
ik_ratio= ik_disc/yk_ds_disc

xk_ds_disc = disc_bs$simulation$xk_ds
mk_ds_disc = disc_bs$simulation$mk_ds

trade_balance_disc= (xk_ds_disc - mk_ds_disc)/yk_ds_disc
```

@@

ik_disc_01 = disc_S1$simulation$ik

c_ratio_01= pconk_ds_disc_01/yk_ds_disc_01
ik_ratio_01= ik_disc_01/yk_ds_disc_01

xk_ds_disc_01 = disc_S1$simulation$xk_ds
mk_ds_disc_01 = disc_S1$simulation$mk_ds

trade_balance_disc_01= (xk_ds_disc_01 - mk_ds_disc_01)/yk_ds_disc_01

@@

```{r}
plot((c_ratio_01 - c_ratio), col= "black", xlab= "Year", ylab= "% Change in gdp", main= "GDP");grid()

plot((ik_ratio_01 - ik_ratio), col= "black", xlab= "Year", ylab= "% Change in gdp", main= "GDP");grid()

plot((trade_balance_disc_01 - trade_balance_disc), col= "black", xlab= "Year", ylab= "% Change in gdp", main= "GDP");grid()
```
